TacticToe: Learning the Game of Tactics

### 2018-01-30 tactictoe_jv.tex
minor

\item $A$ is a partial function from $\mathbb{G} \times \mathbb{T}$ to 
$\mathbb{A}$. It takes a goal and a tactic and returns the node produced by the 
application of the tactic to the goal, if this tactic has been applied to this 
goal. Its support $Support(A)$ is by definition $\lbrace (g,t)\ |\ t \in T(g) 
\rbrace$.
\item if $(g,t) \in Support (A)$ and $A(g,t) = a$, then $t(g) = G(a)$.
\end{itemize}

@@

In order to include the possibly of trying more tactic on $g$ we define the 
widening policy on the parent $a$ for its open goal $g$ to be:

@@

When \tactictoe finds a proof of a goal, it returns a search tree 
$\mathfrak{T}$ where the root node containing this goal is solved.
In order to transform this search tree into a proof script, we need to extract 
the tactics that contributed to the proof and combine them using tactic 
combinators.
\todoi{Define tactic combinators?}
By the design of the search, a single tactic combinator, \texttt{THENL}, is 
sufficient. It combines a tactic $t$ with a list of subsequent ones, in such a 
way that after $t$ is called, for each created goal a respective 
tactic from the list is called.
Here is a formal description of the transformation $Proof$ defined by mutual 
recursion on the goals and nodes of $\mathfrak{T}$:

%\begin{equation*}
%Proof(g) =_{def}
%\begin{cases}
%T(g) & \text{if $t$ is a root},\\
%tac & \text{if $t$ is a leaf},\\
%tac\ \texttt{THENL}\ [P(a_1),\ldots,t_{n-1}] & \text{otherwise.}
%\end{cases}
%
%
%\begin{cases}
%tac & \text{if $t$ is a root and $g$ the unique goal of the root},\\
%tac & \text{if $t$ is a leaf},\\
%tac\ \texttt{THENL}\ [P(a_1),\ldots,t_{n-1}] & \text{otherwise.}
%\end{cases}
%
%
%
%
%\end{equation*}
where $tac$ is the tactic that produced the node, $c$ is the
only successful child of the root and $c_0, \ldots, c_n$ are the 
children of the node produced by the successful tactic.

>>>>

\item $A$ is a partial function from $\mathbb{G} \times \mathbb{T}$ to 
$\mathbb{A}$. It takes a goal and a tactic and returns the node produced by the 
application of the tactic to the goal, if this tactic has been applied to this 
goal. Its support $Support(A)$ is by definition $\lbrace (g,t)\ |\ t \in T(g) 
\rbrace$.
\item If $(g,t) \in Support (A)$, then $t(g) = G(A(g,t))$.
\end{itemize}

@@

In order to include the possibly of trying more tactic on $g$ we define the 
widening policy on the parent $p$ for its open goal $g$ to be:

@@

When \tactictoe finds a proof of a goal, it returns a search tree 
$\mathfrak{T}$ where the root node containing this goal is solved.
In order to transform this search tree into a proof script, we need to extract 
the tactics that contributed to the proof and combine them using tactic 
combinators.
\todoi{Define tactic combinators?}
By the design of the search, a single tactic combinator, \texttt{THENL}, is 
sufficient. It combines a tactic $t$ with a list of subsequent ones, in such a 
way that after $t$ is called, for each created goal a respective 
tactic from the list is called.
Here is a formal description of the transformation defined by mutual 
recursion on goals and nodes of $\mathfrak{T}$ by the respective function 
$P_goal$ and $P_node$:

\begin{equation*}
P_goal(g) =_{def}
\begin{cases}
T(g) & \text{if A(g,T(g)) = \emptyset},\\
T(g) & \texttt{THENL}\ [P(a_1),\ldots,t_{n-1}] & \text{otherwise.}
\end{cases}
%
%
Proof(a) =_def{def}
\begin{cases}
tac & \text{if $t$ is a root and $g$ the unique goal of the root},\\
tac & \text{if $t$ is a leaf},\\
tac\ \texttt{THENL}\ [P(a_1),\ldots,t_{n-1}] & \text{otherwise.}
\end{cases}
\end{equation*}

where $tac$ is the tactic that produced the node, $c$ is the
only successful child of the root and $c_0, \ldots, c_n$ are the 
children of the node produced by the successful tactic.
